---
title: "Introduction to R programming Exercise 1 - Assignment Submission"
author: "Shouvik Majumder"
date: "Last updated on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    
    
---
Submission: Testing to see changes
```{r}

```
1. Assign a set of 100 numbers to a variable x. Make sure it includes some positive and some negative numbers. Display the contents of the vetor afterward. Is it really a vector? Enter is.vector(x) to confirm.

```{r}
x<-seq(-100,100,length=100)
x
is.vector(x)

```

2. Print the 3rd and 6th elements of x with a single command.

```{r}
x[c(3,6)]
```

3. Print (i.e. display) all elements of x that are non-negative.

```{r}
x[x>=0]
```

4.Change the last value of your x vector to a different number. Change the 2nd, 6th, and 10th values of x to 1, 2, 3 with a single command.
    
```{r}
x[length(x)]<-5000
x[c(2,6,10)] <- c(1,2,3)
x
```

5. For each of the following examples determine why the code does not work and correct it. Use R's built in help functions if you have trouble on the second set.
```{r}

my_variable <- 10
my_varıable
```

```{r}
x<-c(2,34,61,21,NA ,32)
y<-c(5,56,789,23,3,90)
z <- mean(x*y, na.rm=TRUE)
z
```






